---
title: "Flexdashboard Code"
author: "Tvisha R. Devavarapu"
date: "2022-10-31"
output: html_document
---

# Set-up
```{r}
library(tidyverse)

library(plotly)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = .6,
  out.width = "90%"
)
```

```{r}
library(p8105.datasets)
data("instacart")

instacart_df =
  instacart %>%
    janitor::clean_names()
```


**1. Most ordered fresh vegetables**

```{r Most ordered fresh veggies}
instacart_df %>% 
  select(product_name, aisle) %>% 
  filter(aisle == "fresh vegetables") %>% 
  group_by(product_name) %>% 
  summarise(counts = n()) %>% 
  filter(counts > 1000) %>% 
  mutate(product_name = fct_reorder(product_name, counts)) %>% 
  plot_ly(x = ~product_name, y = ~counts, type = "bar") %>% 
    layout(title = "<b>Most frequently ordered products (counts > 1000) in the 'Fresh Vegetables' aisle</b>",
           yaxis = list(title = "<b>Counts (# of orders)</b>"),
           xaxis = list(title = "<b>Product</b>", tickangle = 45))
  
```
*Customers on instacart seem to have a preference towards organic produce within the 'Fresh Vegetables' aisle.*


**2. Time-wise trend in overall produce/snacks/personal-care orders**

```{r Time-wise trend in overall produce/snacks/personal-care orders}
instacart_df %>% 
  select(order_hour_of_day, department) %>% 
  mutate(order_hour_of_day = factor(order_hour_of_day)) %>% 
  filter(department %in% c("produce", "snacks", "personal care")) %>% 
  group_by(order_hour_of_day, department) %>% 
  summarise(counts = n()) %>% 
  plot_ly(x = ~order_hour_of_day, y = ~counts,
          type = "scatter", mode = "markers",
          color = ~department, size = ~counts,
          text = ~paste("Time: ", order_hour_of_day, "/24", '<br>Counts:', counts)) %>% 
    layout(title = "<b>Time-wise trends in overall produce/snacks/personal-care orders</b>",
           yaxis = list(title = "<b>Counts (# of orders)</b>"),
           xaxis = list(title = "<b>Time of Day</b>",
                        tickvals = c(0, 3, 6, 9, 12, 15, 18, 21, 23),
                        ticktext = c("12 AM", "3 AM", "6 AM", "9 AM", "12 PM",
                                     "3 PM", "6 PM", "9 PM", "11 PM"),
                        tickangle = 45))
```
*Produce is more frequently ordered than snacks and personal care. 10 AM - 2 PM seems to be time when most of the produce orders are made. For snacks, most products were ordered 11 AM and 2 PM but dipped a little in the time in between. For personal care products, just like snacks, the most likely time to order was 11 AM or 2 PM.*


**3. Top 5 items in Top 10 Aisles**

```{r Top 5 items in Top 10 Aisles - rank as factor ver.}
aisle_counts = 
  instacart_df %>% 
    group_by(aisle) %>% 
    count(aisle) %>%
    arrange(desc(n))

top_10_aisles = aisle_counts$aisle[1:10]

instacart_df %>% 
  filter(aisle %in% top_10_aisles) %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 6) %>% 
  mutate(rank = factor(rank)) %>% 
  arrange(aisle, rank) %>% 
  plot_ly(x = ~aisle, y = ~n, type = "bar", color = ~rank,
          text = ~paste("Name: ", product_name, '<br>Counts:', n)) %>% 
    layout(title = "<b>Top 5 items in Top 10 Aisles</b>",
           yaxis = list(title = "<b>Counts (# of orders)</b>"),
           xaxis = list(title = "<b>Aisle</b>", tickangle = 45),
           legend = list(title = list(text = "<b>Rank</b>")))
```
*Note: Please hover over the individual bars to access the product names!*
